# Dynamic UI

## Exercise 10.1.5.1 {-}

Complete the user interface below with a server function that updates `input$date` so that you can only select dates in `input$year`.

```{r, eval=FALSE}
ui <- fluidPage(
  numericInput("year", "year", value = 2020),
  dateInput("date", "date")
)
```

:::solution
#### Solution {-}

This solution was a little wonky because it required shinyjs for the dateInput to properly update. I [opened up an issue here](https://github.com/rstudio/shiny/issues/2798) since I think this is not the most intuitive answer.

```{r, eval=FALSE}
library(shiny)
library(shinyjs)

ui <- fluidPage(
  useShinyjs() ,
  numericInput("year", "year", value = 2020),
  dateInput("date", "date", value = Sys.Date())
)

server <- function(input, output, session) {
  
  observeEvent(input$year, {
    
    req(input$year) # stop if year is blank
    daterange <- range(as.Date(paste0(input$year, "-01-01")),as.Date(paste0(input$year, "-12-31")))
    updateDateInput(session, "date", min = daterange[1], max = daterange[2] )
    delay(250,  # delay 250ms
          updateDateInput(session,"date",
                          value = daterange[1]
          ))
  })
}

shinyApp(ui = ui, server = server)
```
:::

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

## Exercise 10.1.5.2 {-}

Complete the user interface below with a server function that updates `input$county` choices based on `input$state`. For an added challenge, also change the label from "County" to "Parrish" for Louisana and "Borrough" for "Alaska".

```{r, eval=FALSE}
library(openintro)
states <- unique(county$state)

ui <- fluidPage(
  selectInput("state", "State", choices = states),
  selectInput("county", "County", choices = NULL)
)
```

:::solution
#### Solution {-}

We can use `updateSelectInput` to filter the county choices based on the user selected state. By making the label of `input$county` a reactive, we can use `switch` to change the label when either Alaska or Louisiana is selected.

```{r, eval=FALSE}
library(shiny)
library(tidyverse)
library(openintro)

states <- unique(county$state)
counties <- unique(county$state)

ui <- fluidPage(
  selectInput("state", "State", choices = states),
  selectInput("county", "County", choices = NULL)
)


server <- function(input, output, session) {
  
  label <- reactive({
    switch(input$state,
           "Alaska" = "Burrough",
           "Louisiana" = "Parish",
           "County")
  })
   
  observeEvent( input$state, {
    updateSelectInput(session, "county", label = label(),
                      choices = county %>% 
                        filter(state == input$state) %>%
                        select(name) %>%
                        distinct())
  })

}


shinyApp(ui = ui, server = server)
```
:::

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

## Exercise 10.1.5.3 {-}

Complete the user interface below with a server function that updates `input$country` choices based on the `input$continent`. Use `output$data` to display all matching rows.

```{r, eval=FALSE}
library(gapminder)
continents <- unique(gapminder$continent)

ui <- fluidPage(
  selectInput("continent", "Continent", choices = continents), 
  selectInput("country", "Country", choices = NULL),
  tableOutput("data")
)
```

:::solution
#### Solution {-}

As the question above, we are filtering the country input based on the continent by using `updateSelectInput` in the server. By storing the selected data in a reactive, `selected_data()` we can use the same filtered dataset for our `selectInput` and the table, reducing code redundancy.  

```{r, eval=FALSE}
library(shiny)

library(gapminder)
continents <- unique(gapminder$continent)

ui <- fluidPage(
  selectInput("continent", "Continent", choices = c("", as.character(continents))), 
  selectInput("country", "Country", choices = NULL),
  tableOutput("data")
)

server <- function(input, output, session) {
  
  selected_data <- reactive({
    if(input$continent %in% continents) {
      gapminder %>% 
      filter(continent == input$continent)
    } else {
      gapminder
    }
  })
  
  observeEvent( input$continent, {
    updateSelectInput(session, "country", "Country",
                      choices = selected_data() %>% 
                        select(country) %>%
                        distinct())
  })
  
  output$data <- renderTable({ 
    selected_data() %>% 
      filter(country == input$country) 
  })
}

shinyApp(ui = ui, server = server)
```
:::

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

## Exercise 10.1.5.4 {-}

Extend the previous app so that you can also choose to select no continent, and hence see all countries. You"'ll need to add "" to the list of choices, and then handle that specially when filtering.

:::solution
#### Solution {-}

:::note
Initially setting the choices to `c("", as.character(continents))` allows the user to see all the Country options prior to a continent being selected. That said, once a continent is selected this `""` option is no longer available.
:::

```{r, eval=FALSE}
library(shiny)

library(gapminder)
continents <- unique(gapminder$continent)

ui <- fluidPage(
  selectInput("continent", "Continent", choices = c("", as.character(continents))), 
   # @tanho63:
  # selectInput("continent", "Continent", choices = c("All", as.character(continents))), 
  selectInput("country", "Country", choices = NULL),
  tableOutput("data")
)


server <- function(input, output, session) {
  
  selected_data <- reactive({
    if(input$continent %in% continents) {
      gapminder %>% 
      filter(continent == input$continent)
    } else {
      gapminder
    }
  })
  
  observeEvent( input$continent, {
    
    # @tanho63:
    updateSelectInput(session, "country",
                      choices = unique(selected_data()$country))
  })
  
  output$data <- renderTable({ 
    selected_data() %>% 
      filter(country == input$country) 
  })

}


shinyApp(ui = ui, server = server)
```
:::

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

## Exercise 10.1.5.5 {-}

What is at the heart of the problem described at https://community.rstudio.com/t/29307?

:::solution
#### Solution {-}

Updating all three sliders creates a circular reference!

:::

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

## Exercise 10.2.3.1 {-}

Use a hidden tabset to show additional controls only if the user checks an "advanced" check box.

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

## Exercise 10.2.3.2 {-}

Create that allows the user to select from geom_smooth(), geom_histogram(), or geom_point(). Use a hidden tabset to allow the user to select different options depending on the geom. geom_smooth() should have a text both for the model, and checkbox for whether or not to add standard errors. geom_histogram() should have a numeric input for the bin width, and geom_point() doesn"'t need any additional options.

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

## Exercise 10.2.3.3 {-}

Create a wizard interface that steers the user along the path …

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

## Exercise 10.3.4.1 {-}

Take this very simple app based on the initial example in the chapter:

```{r, eval=FALSE}
ui <- fluidPage(
  selectInput("type", "type", c("slider", "numeric")),
  uiOutput("numeric")
)
server <- function(input, output, session) {
  output$numeric <- renderUI({
    if (input$type == "slider") {
      sliderInput("n", "n", value = 0, min = 0, max = 100)
    } else {
      numericInput("n", "n", value = 0, min = 0, max = 100)  
    }
  })
}
```

How could you instead implement it using dynamic visibility? If you implement dynamic visibility, how could you keep the values in sync when you change the controls?

:::solution
#### Solution {-}

```{r, eval=FALSE}
library(shiny)
parameter_tabs <- tagList(
  tags$style("#params { display:none; }"),
  tabsetPanel(id = "params",
              tabPanel("slider",
                       sliderInput("my_slider", "n", value = 0, min = 0, max = 100)
              ),
              tabPanel("numeric", 
                       numericInput("my_numeric", "n", value = 0, min = 0, max = 100)  
              )
  )
)

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      selectInput("my_selector", "Input Type", 
                  choices = c("slider", "numeric")
      ),
      parameter_tabs,
    ),
    mainPanel()
  )
)

server <- function(input, output, session) {
  
  # if slider changes, update numeric
  observeEvent( input$my_slider, {
    updateNumericInput(session, "my_numeric", value = isolate(input$my_slider))
  })
  
  # if numeric changes update slider
  observeEvent( input$my_numeric, {
    updateSliderInput(session, "my_slider", value = isolate(input$my_numeric))
  })
  
  observeEvent(input$my_selector, {
    updateTabsetPanel(session, "params", selected = input$my_selector)
  }) 
  
}

shinyApp(ui = ui, server = server)
```
:::

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

## Exercise 10.3.4.2 {-}

Explain how this app works. Why does the password disappear when you click the enter password button for the second time?

```{r, eval=FALSE}
ui <- fluidPage(
  actionButton("go", "Enter password"),
  textOutput("text")
)
server <- function(input, output, session) {
  observeEvent(input$go, {
    showModal(modalDialog(
      passwordInput("password", NULL),
      title = "Please enter your password"
    ))
  })

  output$text <- renderText({
    if (!isTruthy(input$password)) {
      "No password"
    } else {
      "Password entered"
    }
  })
}
```

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

## Exercise 10.3.4.3 {-}

Add support for date and date-time columns `make_ui()` and `filter_var()`.

:::solution
#### Solution {-}

In order to complete this, I had to 

1) make a new dummy dataframe I called `x` in order to test for dates
2) include checking for `is.Date` in the `make_ui` and `filter_var` functions
3) Change `tableOutput` and `renderTable` to `DT::renderTableOutput` and `DT::renderTableOutput` because `renderTable` was rendering the dates as numbers and I think this could be because it uses `xtable()` for HTML table rendering?

```{r, eval=FALSE}
# 8.4.3.2
library(shiny)
library(purrr)
library(tidyverse)

make_ui <- function(x, var) {
  if (is.numeric(x)) {
    rng <- range(x, na.rm = TRUE)
    sliderInput(var, var, min = rng[1], max = rng[2], value = rng)
  } else if (is.factor(x)) {
    levs <- levels(x)
    selectInput(var, var, choices = levs, selected = levs, multiple = TRUE)
  } else if (lubridate::is.Date(x)) {
    rng <- range(x, na.rm = TRUE)
    dateInput(var, var, min = rng[1], max = rng[2], value = rng[1])
  } else {
    # No control, so don't filter
    NULL
  }
}


filter_var <- function(x, val) {
  if (is.numeric(x)) {
    !is.na(x) & x >= val[1] & x <= val[2]
  } else if (is.factor(x)) {
    x %in% val
  } else if (lubridate::is.Date(x)) {
    x %in% val
  } else {
    TRUE
  }
}

library(shiny)

dfs <- keep(ls("package:datasets"), ~ is.data.frame(get(.x, "package:datasets")))

# add a dataframe with dates in it since I cant find one in the datasets above
# rep 5 dates five times, each include 1 factor a-e
x <- data.frame(date = c(rep(as.Date("2020/1/1"), 5),
                         rep(as.Date("2020/2/2"), 5),
                         rep(as.Date("2020/3/3"), 5),
                         rep(as.Date("2020/4/4"), 5),
                         rep(as.Date("2020/5/5"), 5)),
                fac = as.factor(c("a", "b", "c", "d", "e")))

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      #selectInput("dataset", label = "Dataset", choices = c(dfs, "x")),
      uiOutput("filter")
    ),
    mainPanel(
      DT::dataTableOutput("data")
    )
  )
)

server <- function(input, output, session) {
  
  # data is either my dummy dataset or from datasets
  data <- reactive(x)
  
  vars <- reactive(names(data()))
  
  output$filter <- renderUI(
    # take eahc column name and make ui
    # data()[[.x]] is each column
    # and .x is each column name (vars())
    map(vars(), ~ make_ui(data()[[.x]], .x))
  )
  
  selected <- reactive({
    # take each column name and filer var
    # with the first argument the column in the data
    # and the second argument the input$vars()
    # so for date check that input[[date]] in data[[1]]
    each_var <- map(vars(), ~ filter_var(data()[[.x]], input[[.x]]))
    
    # notes from @mapaulacaldas
    # collapse list of TRUE and FALSE using `&`
    # conditions <- list(TRUE, TRUE, TRUE, FALSE)
    # purrr::reduce(conditions, `&`) ==
    # ((conditions[[1]] & conditions[[2]]) & conditions[[3]]) & conditions[[4]]
    reduce(each_var, `&`)
  })
  
  # subset the data by the vars that are true
  output$data <- DT::renderDataTable(data()[selected(), ])
}
# Run the application 
shinyApp(ui = ui, server = server)
```
:::

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

## Exercise 10.3.4.4 {-}

(Advanced) If you know the S3 OOP system, consider how you could replace the if blocks in `make_ui()` and `filter_var()` with generic functions.

:::solution
#### Solution {-}

```{r, eval=FALSE}
library(shiny)
library(purrr)

make_ui <- function(obj, var) { UseMethod("make_ui") }

make_ui.numeric <- function(x, var) {
  rng <- range(x, na.rm = TRUE)
  sliderInput(var, var, min = rng[1], max = rng[2], value = rng)
}

make_ui.factor <- function(x, var) { 
  levs <- levels(x) 
  selectInput(var, var, choices = levs, selected = levs, multiple = TRUE)
}

make_ui.default <- function(x, var) { NULL }

filter_var <- function(x, val) { UseMethod("filter_var") }
filter_var.numeric <- function(x, val) { !is.na(x) & x >= val[1] & x <= val[2] }
filter_var.factor <- function(x, val) { x %in% val }
filter_var.default <- function(x, val) { TRUE }

dfs <- keep(ls("package:datasets"), ~ is.data.frame(get(.x, "package:datasets")))

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      selectInput("dataset", label = "Dataset", choices = dfs),
      uiOutput("filter")
    ),
    mainPanel(
      tableOutput("data")
    )
  )
)
server <- function(input, output, session) {
  data <- reactive({
    get(input$dataset, "package:datasets")
  })
  
  vars <- reactive(names(data()))
  
  output$filter <- renderUI(
    map(vars(), ~ make_ui(data()[[.x]], .x))
  )
  
  selected <- reactive({
    each_var <- map(vars(), ~ filter_var(data()[[.x]], input[[.x]]))
    reduce(each_var, `&`)
  })
  
  output$data <- renderTable(head(data()[selected(), ], 12))
}

shinyApp(ui = ui, server = server)
```
:::

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

## Exercise 10.3.4.5 {-}

(Hard) Make a wizard that allows the user to upload their own dataset. The first page should handle the upload. The second should handle reading it, providing one drop down for each variable that lets the user select the column type. The third page should provide some way to get a summary of the dataset.

:::solution
#### Solution {-}

:::note
I wasn't really sure what was meant by "some way to get a summary of the dataset" So I'm just using the summary function.
:::

```{r, eval=FALSE}
library(shiny)
library(readr)

make_dropdown <- function(name_of_vector) {
  selectInput(inputId = name_of_vector, label =  name_of_vector, choices = 
                c("numeric", "character", "logical"))
}  

ui <- fluidPage(
  tags$style("#wizard { display:none; }"),
  tabsetPanel(id = "wizard",
              tabPanel("page1", 
                       fileInput("data_input", "input"),
                       actionButton("page12", "next")
              ),
              tabPanel("page2",
                         sidebarLayout(
                           sidebarPanel(
                             uiOutput("type_of")
                           ),
                           mainPanel(
                             tableOutput('type_table')
                           )),
                       actionButton("page21", "prev"),
                       actionButton("page23", "next")
              ),
              tabPanel("page3", 
                       tableOutput("summary_table"),
                       actionButton("page32", "prev")
              )
  )
)

server <- function(input, output, session) {
  
  ################ WIZARD  ###############################
  
  switch_tab <- function(page) {
    updateTabsetPanel(session, "wizard", selected = page)
  }
  
  observeEvent(input$page12, switch_tab("page2"))
  observeEvent(input$page21, switch_tab("page1"))
  observeEvent(input$page23, switch_tab("page3"))
  observeEvent(input$page32, switch_tab("page2"))
  
  ##################### FILE INPUT #######################
  
  dat <- reactive({
    req(input$data_input)
    read.csv(input$data_input$datapath)
  })
  
  ##################### TABLE TYPE #######################
  
  # make a dropdown using the names of each column
  output$type_of <- renderUI({ map(names(dat()), ~ make_dropdown(.x)) })
  
  
  # switch the type of column based on the input
  # name of vector == "Sepal.Length"
  # vector == Sepal.Length
  change_type <- function(vector, name_of_vector) {
    switch(input[[name_of_vector]],
           "numeric" = vector <- as.numeric(vector),
           "character" = vector <- as.character(vector),
           "logical" = vector <- as.complex(vector)
    )
  }
  
  # convert the supplied data to a list
  # use imap because it is a condensed version o map
  # with two arguments == x & name_of_x
  # so we don't need to supply it arguments beyond the list!
  df<- reactive({
    dat() %>% 
      as.list() %>% 
      imap(change_type) %>% 
      as_tibble()
  })
  
  # create an output of the data's names
  # and their types
  output$type_table <- renderTable(data.frame(
    names = names(df()),
    type = map_chr(df(), function(x) typeof(x)))
  )
  
  ##################### TABLE OUTPUT #####################
  
  output$summary_table <- renderTable( summary(df()) )
}

shinyApp(ui = ui, server = server)
```
:::
