# Graphics

### Exercise 7.5.1 {-}

Make a plot with click handle that shows all the data returned in the input.

:::solution
#### Solution {-}

We can use the `allRows` argument in `nearPoints` to see the entire data and
add a boolean column that will be true `TRUE` for the given point (i.e., row)
that was clicked.

```{r, eval=FALSE}
library(shiny)
library(ggplot2)

ui <- fluidPage(
  plotOutput("plot", click = "plot_click"),
  tableOutput("data")
)

server <- function(input, output, session) {
  output$plot <- renderPlot({
    ggplot(mtcars, aes(wt, mpg)) + geom_point()
  }, res = 96)
  
  output$data <- renderTable({
    nearPoints(mtcars, input$plot_click, allRows = TRUE)
  })
}

shinyApp(ui, server)
```
:::

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

### Exercise 7.5.2 {-}

Make a plot with click, dblclick, hover, and brush output handlers and nicely
display the current selection in the sidebar. Plot the plot in the main panel.

:::solution
#### Solution {-}

We can use the `nearPoints` function to extract the data from `plot_click`,
`plot_dbl`, and `plot_hover`. We need to use the function `brushedPoints` to
extract the points within the `plot_brush` area.

To 'nicely' display the current selection, we will use `dataTableOutput`.

```{r, eval=FALSE}
library(shiny)
library(ggplot2)

# Set options for rendering DataTables.
options <- list(
  autoWidth = FALSE,
  searching = FALSE,
  ordering = FALSE,
  lengthChange = FALSE,
  lengthMenu = FALSE,
  pageLength = 5, # Only show 5 rows per page.
  paging = TRUE, # Enable pagination. Must be set for pageLength to work.
  info = FALSE
)

ui <- fluidPage(
  
  sidebarLayout(
    sidebarPanel(
      width = 6,
      
      h4("Selected Points"),
      dataTableOutput("click"), br(),

      h4("Double Clicked Points"),
      dataTableOutput("dbl"), br(),
      
      h4("Hovered Points"),
      dataTableOutput("hover"), br(),
      
      h4("Brushed Points"),
      dataTableOutput("brush")
    ),
    
    mainPanel(width = 6,
              plotOutput("plot",
                         click = "plot_click",
                         dblclick = "plot_dbl",
                         hover = "plot_hover",
                         brush = "plot_brush")
    )
  )
)

server <- function(input, output, session) {
  
  output$plot <- renderPlot({
    ggplot(iris, aes(Sepal.Length, Sepal.Width)) + geom_point()
  }, res = 96)
  
  output$click <- renderDataTable(
    nearPoints(iris, input$plot_click),
    options = options)
  
  output$hover <- renderDataTable(
    nearPoints(iris, input$plot_hover),
    options = options)
  
  output$dbl <- renderDataTable(
    nearPoints(iris, input$plot_dbl),
    options = options)
  
  output$brush <- renderDataTable(
    brushedPoints(iris, input$plot_brush),
    options = options)
}

shinyApp(ui, server)
```
:::

<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->
<!---------------------------------------------------------------------------->

### Exercise 7.5.3 {-}

Compute the limits of the distance scale using the size of the plot.

```{r, eval=FALSE}
output_size <- function(id) {
  reactive(c(
    session$clientData[[paste0("output_", id, "_width")]],
    session$clientData[[paste0("output_", id, "_height")]]
  ))
}
```
:::
