# Modules

## 15.6.1 {-}

:::question
Example passing input$foo to reactive and it not working.
:::
  
TODO: I don't really know what this means

## 15.6.2 {-}

:::question
Rewrite `selectVarServer()` so that both data and filter are reactive. Pair it with a app function that lets the user pick the dataset with the dataset module, a function with an `inputSelect()` that lets the user filter for numeric, character, or factor variables.
:::

## 15.6.3 {-}

:::question
The following code defines output and server components of a module that takes a numeric input and produces a bulleted list of three summary statistics. Create an app function that allows you to experiment with it. The app function should take a data frame as input, and use `numericVarSelectInput()` to pick the variable to summarise.

```{r, eval=FALSE}
summaryOuput <- function(id) {
  tags$ul(
    tags$li("Min: ", textOutput(NS(id, "min"), inline = TRUE)),
    tags$li("Max: ", textOutput(NS(id, "max"), inline = TRUE)),
    tags$li("Missing: ", textOutput(NS(id, "n_na"), inline = TRUE))
  )
}

summaryServer <- function(id, var) {
  moduleServer(id, function(input, output, session) {
    rng <- reactive({
      req(var())
      range(var(), na.rm = TRUE)
    })

    output$min <- renderText(rng()[[1]])
    output$max <- renderText(rng()[[2]])
    output$n_na <- renderText(sum(is.na(var())))
  })
}
```
:::

## 15.6.4 {-}

:::question
The following module input provides a text control that lets you type a date in ISO8601 format (yyyy-mm-dd). Complete the module by providing a server function that uses output$error to display a message if the entered value is not a valid date. The module should return a Date object for valid dates. (Hint: use strptime(x, "%Y-%m-%d") to parse the string; it will return NA if the value isn’t a valid date.)
:::

```{r, eval=FALSE}
ymdDateUI <- function(id, label) {
  label <- paste0(label, " (yyyy-mm-dd)")

  fluidRow(
    textInput(NS(id, "date"), label),
    textOutput(NS(id, "error"))
  )
}
```


## 15.6.5 {-}

:::question
In `radioExtraServer()`, return a list that contains both the value and whether or not it came from other
:::

## 15.6.6 {-}

:::question
In `wizardServer()` verify that the namespacing has been set up correctly by using two or more wizards in a single add, and checking that you can navigate through each wizard independently.
:::
